A Novel Comprehensive Quality Evaluation Model in Automated Semantic Web Service Composition

### 2016-10-20 paper.tex
update

\subsection{Related Work}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focus particularly on functional requirements and negect non-functional requirements. This approach utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking. Since semantic descriptions are introduced into web service, which is expressed in ontologies, the semantic matchmaking is to considered to seek similarity of parameters (i.e., input and output) of web services and pair a mapping between two knowledge representations encoded utilising the same ontology \cite{lecue2006formal}. In \cite{shet2012new}, the author surveyed three approaches the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods. A new similarity measure based on edge counting is introduced in a Ontology in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formular \ref{equation1}, where $\lambda$ = 1 (default value as 0).

@@

In \cite{lecue2009optimizing}, web services are connected as an semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which apply one possible measure for similarity degree on nodes information demonstrated as Common Description rate of a semantic link in Formula \ref{equation2}. Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$and Least Subsume $lcs(Out_{s_i},In_{s_j})$. They chained the web service in five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. The quality of the semantic link is estimated as quality criteria $q_{m}$(i.e. either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection)) associated with their corresponding quality of vector $q_{cd}$ \ref{equation2}. The model is defined as follows.
\begin{equation}
\label{equation2}
q(sl{_{i,j}}) \stackrel{.}{=} (q_{mt}(sl_{i,j}), \  q_{cd}(sl_{i,j}))
\end{equation}
\begin{equation}
q_{cd}(sl{_{i,j}})={=} \frac{|lcs(Out_{s_i},In_{s_j})|}{|In_{s_{x}} \setminus Out_{s{_y}} \stackrel{.}| +|lcs(Out_{s_i},In_{s_j})| }
 \label{equation3}
\end{equation}

However, the weakness of this approach for semantic link quality is that calculating Extra Description and Least Subsume of out-input request requires well and complete defined DL in knowledge representation in the different domains, which makes it nearly impossible to be widely applied to semantic matchmaking measures in today's' web services application. Additionally, in their semi-auto workflow approach, they do not consider data-flow compatible and automated service composition.

\textbf{QoS-aware EC approaches}.
Evolution Computing techniques are considered to be more effective for solving globally optimisation problem. Genetic Programming (GP) approaches \cite{da2015graphevol,da2016particle} are typical EC techniques widely applied to fully automated web service composition, which utilises a tree representation that service as the terminal nodes, and composite constructs as the functional nodes. The crossover and mutation process reproduce various individuals with ensuring correctness of structure. In \cite{yu2013adaptive}, the author optimises the quality of the overall composition by a complex fitness function, which is also liable for correctness in functionality through penalising solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, this approach is to find a optimised web service queue in the way of searching best location using PSO for optimised QoS, that service queue is involved in building a graph representation of web service composition later. However, the neglecting of leveraging the semantic difference between composite service output and customers' request could lead to the lower quality of functionality matchmaking with best quality of service in QoS-awaren web service composite paper \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph}. For example, a client asks for a particular AI textbook while output of the composte web service provides a general book. In this scenario, the output is a too broad consequences that have no meaning for the customers, even though web services are selected for a excellent composite QoS consideration. Therefore, we fill the gap to provide a more applicable approach to evaluate an overall quality in this paper.

\section{QoS-aware Semantic Autoamted Web Serivce Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
On the support of the representation of our solution, in this section, we introduce our evaluation model in a graph-based representation for QoS-aware automatic semantic web service composition utilising PSO, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the several steps included. The composite process is triggered by a composite goal defined in Subection \ref{problemDes}, which demonstrate customers requirements in terms of functional and non-functional requirement. The previous one is well defined as an overall input-output requirement, and the later one is the users' accepted quality of service. Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for building graph representations. The second step of selecting relevant web services contributes to shrink the size of participated web services for dimensions of particles involved in future optimised problem. In the third step, a service composition graph randomly built up with considering the QoS and matchmaking quality. This graph building is interleaved with semantic matchmaking for services. The output of one service and its associated input of another service is calculated in the matchmaking phase where semantic matchmaking quality are measured which will be explained in Subsection \ref{qulityModel}. The further optimization of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building. This approach \cite{da2016particle} is an indirect representation of web service composition that constructing a graph-based composite service composition.

\subsection{QoS-aware Semantic Web Service Composition algorithm} \label{pso_algorithm}
\begin{algorithm}[!htb]
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \let\oldnl\nl% Store \nl in \oldnl
\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
 \LinesNumbered
	\textbf{1.} Randomly initialise each particle in the swarm.\\
	\nonl \While {max. iterations not met}{
		\ForAll{particles in the swarm}{
			\textbf{2.} Sort partcile's postion vector as a service queue in ascending order\\
			\textbf{3.} Initialise OutputSet with Task Input\\
			\textbf{4.} Initialise a graph with a startNode associated with Task Input as its output\\
			\nonl \While {max. OutputSet not contains Task Input}{
				\textbf{5.} Get web service from service queue\\
				\If{All inputs of current web service satisfied with output from outputSet}{
					\textbf{6.} Create and connect service edge associated with matchmaking quality to graph.\\
					\textbf{7.} Create and connect node(current web serivce) to graph.\\
					\textbf{8.} Remove current web service fromt the queue.\\
					\textbf{9.} Update OutputSet with outputs current web service.\\
				}
				\textbf{10.} Get next web service from service queue\\
			}
			\textbf{11.} Connect endNode the graph\\
			\textbf{12.} Remove dangle services from the graph\\
			\textbf{13.} Remove dangle edges\\
			\textbf{14.} Aggregation of semantic matchmaking and QoS\\
			\textbf{15.} Calculate the particle's fitness.\\
			\Indp $fitness_i = w_1SDst + w_2A_i + w_3R_i + w_4(1 - T_i) + w_5(1 - C_i)$ where $\sum_{i=1}^{5} w_i = 1$ \\
			\eIf{fitness value better than pBest}{
				\textbf{16.} Assign current fitness as new pBest.\\
			}{
				\textbf{17.} Keep previous pBest.\\
			}		
		}
		\textbf{18.} Assign best particle's pBest value to gBest, if better than gBest.\\
		\textbf{19.} Calculate the velocity of each particle according to the equation:\\
		\Indp $v_{id} = v_{id} + c_1 * rand() * (p_{id} - x_{id}) + c_2 * rand() * (p_{gd} - x_{id})$\\
		\Indm \textbf{19.} Update the position of each particle according to the equation:\\
		\Indp $x_{id} = x_{id} + v_{id}$\\
	}

 \caption{Steps of graph-based PSO optimisation technique.}
\label{psoSteps}
\end{algorithm}
The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} and a graph-building technique \cite{blum1997fast} with our comprehensive quality evaluation model. The idea of that is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to figure out the optimised location of the particle. In PSO, the dimension of the particle is set up as the same as the number of relevant web services shrunk from serivce repository, and all of them are mapped to the particle location, put in a service queue and sorted in ascending order. The second method is to decode a corresponding graph built from that service queue. and it is a forward graph-building technique from a start node to the end node, we select and connect web services to startNode if this web service can satisfy the given Task input initialised in a Output Set, and this Output Set is updated after adding web service to the graph, later on, we services are keeping being selected and added if its added services' outputs in the Output Set could be satisfied, if the any outputs in the Output Set meets the Task's requriment, we end up graph building. In addition, dangle services and edges shoud be removed. At last, fitness value can be calculated by the construct-based aggregation.

\subsection{Semantic matchmaking}
The semantic matchmaking is achieved by utilising semantic annotation with OWL and MECE ontologies \cite{bleul2008self} with OWL and XWL format respectively. In OWL,  the semantics specifies the both concepts and individuals in forms of classes and instances but limited to taxonomies. The semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matchingmaking process is demonstrated in Figure \ref{matchmaking}.

@@

The semantic matchmaking transfer a function match (OutputS1, InputS2 ) to a pair of concept match (C2, C3) for the two web services defined in Section \ref{semantic Web service Discovery}. The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for the two its reasoning is also calculated in the quality model in the following Section ref{qulityModel}. The advantage of utilising semantic matchmaking is to enable a reasonable connection between two web services from different service providers to find more service solutions with better QoS.

\subsection{Comprehensive quality model and aggregation matrix}\label{qulityModel}
In this paper, we proposed a semantic matchmaking model to evaluate the semantic quality of two matched web services. Then we fill the gap of current prevailing QoS-aware optimisation consideration in the fully automated composition approach, which has not considered the quality of matchmaking for service selection.

\textbf{Semantic matchmaking model}. Due to the discretizational characteristics of different match types, the match type quality is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, so that match type is considered to be one factor for the semantic quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In our paper, it could be used to estimate the parameter concepts similarity between the output and input request for selecting the highest semantic-closeness web services. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Equation \ref{equation4}.$q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} (i.e. either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection)), and $q(s_ {similarity})$ is Equation \ref{equation1}.

@@

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional attributes of composite web service. The non-functional properties typically refer to availability, reliability, cost and response time, which are given by service providers. Consequently, the comprehensive quality model integrated the semantic matchmaking quality and quality of service in Equation \ref{equation5}, which could be broken down into Equation \ref{equation6}.

@@

\textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties. Typically, two web services are connected by more than one parameter-related concepts. In details, edge-level quality aggregation is determined by the mean of parameter-related concept quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edege-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition. The calculation of QoS aggregation is similar to \cite{cardoso2004quality} while semantic matchmaking aggregation is adopted from \cite{lecue2009optimizing}.

@@

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst. In addtion, aggregate value of each parameters must be normalised between 0 and 1. In details, $MT$, $S$, $A$, and $R$ are calculated in Formula \ref{equation8} while $T$ and $C$ are calculated in Formula \ref{equation9}.

\begin{equation}
\label{equation7}
fitness_i = w_1MT + w_2S + w_3A_i + w_4R_i + w_5(1 - T_i) + w_6(1 - C_i)
\end{equation}

\noindent where $\sum_{i=1}^{6} w_i = 1$
\\\\
\begin{equation}
\label{equation8}
normalise(MT, S, A, or R) = 
\begin{cases}
	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}

\begin{equation}
\label{equation9}
normalise(T or C) = 
\begin{cases}
	\frac{max - value}{max - min} & \text{ if }max - min \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objective of the evaluation are: 1) measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and explore the impact of the semantic matchmaking that contributes to overall composition quality. 2) compare the optimised sollutions with using comprehensive evaluation model with using QoS-aware evaluation model to reveal the advantages of our novel method.

@@

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation was done using the composite service approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Section \ref{qulityModel}. The parameters were chosen based on general settings from \cite{shi2001particle}, In PSO approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph. we run 30 times independently for each dataset. In addition, weights setting are more flexible defined by users' preferences. Simplely, we configure weights of fitness function as same leverage for balancing functional side and nonfunctional side. Therefore, W1 and W2 are equals to 0.1 and 0.4 entirety 0.5,  and W3, W4, W5, W6 are all set to 0.125 summed 0.5.

@@

We also investigate the variation in functional quality part including two subfactors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third groups in Figure \ref{exp_fitnessvalue}.  In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found,  and further calculated their mean over 30 independent runs respectively. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend. However, there are some slight fluctuations over the generations, and it could be reasonably treated as a typical situation that theoretically single objective function prevents selecting the lowest semantic matchmaking quality without granting for the excellent, yet the combination of all the influential functional quality part evolved towards an optimised solution.

>>>>

\subsection{Related Work}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements and negect non-functional requirements. This approach utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking. Since semantic descriptions are introduced into web service, which is expressed in ontologies, the semantic matchmaking is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}. In \cite{shet2012new}, the author surveyed three approaches the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods. A new similarity measure based on edge counting is introduced in a Ontology in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formular \ref{equation1}, where $\lambda$ = 1 (default value as 0).

@@

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}. And Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are also required to be pre-calculated in Formula \ref{equation2}. They chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$, either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.

\begin{equation}
q_{cd}(sl{_{i,j}})={=} \frac{|lcs(Out_{s_i},In_{s_j})|}{|In_{s_{x}} \setminus Out_{s{_y}} \stackrel{.}| +|lcs(Out_{s_i},In_{s_j})| }
 \label{equation2}
\end{equation}

\begin{equation}
\label{equation3}
q(sl{_{i,j}}) \stackrel{.}{=} (q_{mt}(sl_{i,j}), q_{cd}(sl_{i,j}))
\end{equation}

However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined DL in the knowledge representation system. for example, both service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2 are needed. This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications. Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method. Therefore, we introduce a more applicable evaluation model in a full automated semantic web service composition.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition. GP-based approach utilises tree representations, on which service as represented as terminal nodes, and composite constructs as the functional nodes. The crossover and mutation operations reproduce various individuals while ensuring correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is looked for using PSO considering optimising QoS for building up service queue, then the web services in this service queue are selected to build up a graph representation of web service composition. However, the composite solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the data requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and their similarity when evaluate an overall quality of composite service.

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model automated QoS-ware semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO based approach, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the several steps included. The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which demonstrate customers requirements in terms of functional and non-functional requirement. The previous functional one is defined as $F(T_{Input}, T_{Output})$ , and the later nonfunctional one is the users' accepted level of QoS. Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for designing service composition via building graphs. The second step selects relevant web services related to services request. This leads to a shrunken service repository that is used by PSO-based algorithm. In the third step, a service composition graph randomly built up with considering the QoS and matchmaking quality. This graph building is interleaved with semantic matchmaking for services. The output of one service and its associated input of another service is calculated in the matchmaking phase where semantic matchmaking quality are measured which will be explained in Subsection \ref{qulityModel}. The further optimisation of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building. This approach \cite{da2016particle} is an indirect representation of web service composition that constructing a graph-based composite service composition.

\subsection{QoS-aware Semantic Web Service Composition algorithm} \label{pso_algorithm}
\begin{algorithm}[!htb]
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \let\oldnl\nl% Store \nl in \oldnl
\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
 \LinesNumbered
	\textbf{1.} Randomly initialise each particle in the swarm.\\
	\nonl \While {max. iterations not met}{
		\ForAll{particles in the swarm}{
			\textbf{2.} Sort particle's position vector as a service queue in ascending order\\
			\textbf{3.} Initialise OutputSet with Task Input\\
			\textbf{4.} Initialise a graph with a startNode associated with Task Input as its output\\
			\nonl \While {max. OutputSet not contains Task Input}{
				\textbf{5.} Get web service from service queue\\
				\If{All inputs of current web service satisfied with output from outputSet}{
					\textbf{6.} Create and connect service edge associated with matchmaking quality to graph.\\
					\textbf{7.} Create and connect node(current web service) to graph.\\
					\textbf{8.} Remove current web service from the queue.\\
					\textbf{9.} Update OutputSet with outputs current web service.\\
				}
				\textbf{10.} Get next web service from service queue\\
			}
			\textbf{11.} Connect endNode the graph\\
			\textbf{12.} Remove dangle services from the graph\\
			\textbf{13.} Remove dangle edges\\
			\textbf{14.} Aggregation of semantic matchmaking and QoS\\
			\textbf{15.} Calculate the particle's fitness.\\
			\Indp $fitness_i = w_1SDst + w_2A_i + w_3R_i + w_4(1 - T_i) + w_5(1 - C_i)$ where $\sum_{i=1}^{5} w_i = 1$ \\
			\eIf{fitness value better than pBest}{
				\textbf{16.} Assign current fitness as new pBest.\\
			}{
				\textbf{17.} Keep previous pBest.\\
			}		
		}
		\textbf{18.} Assign best particle's pBest value to gBest, if better than gBest.\\
		\textbf{19.} Calculate the velocity of each particle according to the equation:\\
		\Indp $v_{id} = v_{id} + c_1 * rand() * (p_{id} - x_{id}) + c_2 * rand() * (p_{gd} - x_{id})$\\
		\Indm \textbf{19.} Update the position of each particle according to the equation:\\
		\Indp $x_{id} = x_{id} + v_{id}$\\
	}

 \caption{Steps of graph-based PSO optimisation technique.}
\label{psoSteps}
\end{algorithm}
The overall algorithm investigated here is a combination of a simple forward decoding PSO \cite{da2016particle} and a graph-building technique \cite{blum1997fast} with our comprehensive quality evaluation model. The idea is to translate the particle location into a service queue as an indirect representation of service composition graph, finding the best fitness of the composite service solution is to discover the optimised location of the particle. In PSO, the dimension of the particle is set up as the same as the number of relevant web services in the shrunken service repository, each of which is mapped to a location in a particle, put services in a queue and sort in ascending order. The second method is to decode a corresponding graph built from that service queue using a forward graph-building technique from a start node to the end node. We select and connect web services to the startNode if this web service can satisfy the given Task input, and an Output Set is initialised and kept updating with outputs from new added web services in the graph, later on, we services are keeping being selected and added if services' inputs could be satisfied by any output in the Output Set, if the Output Set contains the Task's required outputs, we end up graph building. In addition, dangle service nodes and edges should be removed. At last, fitness value can be calculated by the construct-based aggregation.

\subsection{Semantic matchmaking}
The semantic matchmaking is achieved by utilising semantic annotation with OWL and MECE ontologies \cite{bleul2008self} with OWL and XWL format respectively. In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances but limited to taxonomies. The semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

@@

The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}. The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for the two its reasoning is also calculated in the quality model in the following Section ref{qulityModel}. The advantage of utilising semantic matchmaking is to enable a reasonable connection between two web services from different service providers to find more service solutions with better QoS.

\subsection{Comprehensive quality model and aggregation matrix}\label{qulityModel}
In this paper, we propose a semantic matchmaking model to evaluate the semantic quality of two matched web services, this fill the gap of current prevailing QoS-aware optimisation consideration in the fully automated composition approaches, which has not considered the quality of matchmaking for service selection.

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types, which is driven by the cost of  data type integration and manipulation \cite{lecue2009optimizing}, so that match type is considered to be one factor for the semantic quality. Another factor in our proposed model is concept similarity, which could be evaluate based on edge counting method defined by \cite{shet2012new}, a taxonomy based measurement for ontology matching, In this paper, it could be used to estimate the parameter concepts similarity between the output and input of a request for selecting web services with close semantic matching. Therefore, given the quality match type and the similarity of two parameters, the semantic matchmaking quality is defined as Equation \ref{equation4}.$q(s_ {matchType})$ is set up as the same as the quality of the semantic link in literature \cite{lecue2009optimizing} (i.e. either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection)), and $q(s_ {similarity})$ is Equation \ref{equation1}.

@@

\textbf{Comprehensive quality model}. Compared to QoS evaluation model, the comprehensive quality model is established to investigate both functional and non-functional reguirements of composite web service. The non-functional properties typically refer to availability, reliability, cost and response time, which are given by service providers. Consequently, the comprehensive quality model integrated the semantic matchmaking quality and quality of service in Equation \ref{equation5}, which could be broken down into Equation \ref{equation6}.

@@

\textbf{Quality aggregate matrix}.The quality aggregation is defined based on the constructs of composite web services on the criteria of functional and non-functional properties. Typically, two web services are connected by more than one parameter-related concepts. In details, edge-level quality aggregation is determined by the mean of parameter-related concept quality in both semantic match type and similarity respectively, and construct-level quality is further calculated based on the edge-level quality aggregation following the rules in Table \ref{table1}, which is the quality aggregate matrix for semantic web service composition. The calculation of QoS aggregation is similar to \cite{cardoso2004quality} while semantic matchmaking aggregation is adopted from \cite{lecue2009optimizing}.

@@

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst. In addition, aggregate value of each parameters must be normalised between 0 and 1. In details, $MT$, $S$, $A$, $R$, $T$, and $C$ are normalised in Formula \ref{equation8}.

\begin{equation}
\label{equation7}
Fitness = w_1MT + w_2S + w_3A + w_4R + w_5(1 - T) + w_6(1 - C)
\end{equation}

\noindent where $\sum_{i=1}^{6} w_i = 1$
\\\\
\begin{equation}
\label{equation8}
N(Q_{k}) = 
\begin{cases}
	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objective of the evaluation are: 1) measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and explore the impact of the semantic matchmaking that contributes to overall composition quality. 2) compare the optimised solutions with using comprehensive evaluation model with using QoS-aware evaluation model to reveal the advantages of our novel method.

@@

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation was done using the composite service approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Section \ref{qulityModel}. The parameters were chosen based on general settings from \cite{shi2001particle}, In PSO approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph. we run 30 times independently for each dataset. In addition, weights setting are more flexible defined by users' preferences. Simply, we configure weights of fitness function as same leverage for balancing functional side and nonfunctional side. Therefore, W1 and W2 are equals to 0.1 and 0.4 entirety 0.5,  and W3, W4, W5, W6 are all set to 0.125 summed 0.5.

@@

We also investigate the variation in functional quality part including two sub factors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third groups in Figure \ref{exp_fitnessvalue}.  In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found,  and further calculated their mean over 30 independent runs respectively. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend. However, there are some slight fluctuations over the generations, and it could be reasonably treated as a typical situation that theoretically single objective function prevents selecting the lowest semantic matchmaking quality without granting for the excellent, yet the combination of all the influential functional quality part evolved towards an optimised solution.
